Paper 1

### 2022-06-14 scripts/Paper 1.Rmd
u

rainfall <- rbind.fill(rainfall.2merge, rainfall.SP)
rainfall$month <- as.factor(rainfall$month)

@@

```{r, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}
SWC <- ggplot(input.daily, aes(jday, SWC, group = Year)) +
  geom_line(aes(color = Year), size = 1.5)+
  xlab('Julian day of year') +
  ylab('SWC %') +
  theme_classic() + 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14))
```

@@

NEE.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly NEE")+
  xlab("month")+
  theme_classic()

@@

```{r cumulative fluxes}
cum.co2fluxes <- input.daily %>%
  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, jday, Year, month)
```

>>>>

@@

```{r, echo=FALSE, message = FALSE, fig.width = 8, fig.height = 4}
(SWC <- ggplot(input.daily, aes(jday, SWC, group = Year)) +
  geom_line(aes(color = Year), size = 1.5)+
  xlab('Julian day of year') +
  ylab('SWC %') +
  theme_classic() + 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.text = element_text(size = 13),
          legend.title = element_text(size = 14)))
```

@@

NEE.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
         scale_x_discrete(limits = month.abb) +

  ylab("Monthly NEE")+
  xlab("month")+
  theme_classic()

@@

```{r cumulative fluxes, fig.width = 10, fig.height = 6}
cum.co2fluxes <- input.daily %>%
  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, jday, Year, month) %>% 
  group_by(Year) %>% 
  mutate(NEEcum = cumsum(NEE_LT.gC),
         GPPcum = cumsum(GPP_LT.gC),
         ERcum = cumsum(ER_LT.gC))

(NEEcum.p <-cum.co2fluxes %>% 
  ggplot(., aes(jday, NEEcum, color = Year)) +
  geom_line(size = 1)+
  ylab(bquote('Cumulative NEE (g C' ~m^-2~')'))+
  xlab("Julian day of year")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.position = "none"))

(NEE.time <- input.daily %>% 
  ggplot(., aes(jday, NEE_LT.gC, color = Year)) +
  geom_line(size = 1)+
  ylab(bquote('Cumulative NEE (g C' ~m^-2~ day^-1*')'))+
  xlab("Julian day of year")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.position = "none"))

(NEE.bar <- NEE.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
         scale_x_discrete(limits = month.abb) +
  ylab(bquote('Total monthly NEE (g C' ~m^-2~')'))+
  xlab("Month")+
  theme_classic() + 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.position = "none"))

(GPPcum.p <-cum.co2fluxes %>% 
  ggplot(., aes(jday, GPPcum, color = Year)) +
  geom_line(size = 1)+
  ylab(bquote('Cumulative GPP (g C' ~m^-2~')'))+
  xlab("Julian day of year")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.position = "none"))

(ERcum.p <-cum.co2fluxes %>% 
  ggplot(., aes(jday, ERcum, color = Year)) +
  geom_line(size =1)+
  ylab(bquote('Cumulative ER (g C' ~m^-2~')'))+
  xlab("Julian day of year")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13),
          legend.position = "none"))

Fig2 <- plot_grid(NEE.bar, NEEcum.p,
             GPPcum.p, ERcum.p, ncol = 2, rel_heights = c(0.5, 0.5, 0.5, 0.5))

Fig2
tiff("Fig2.tiff", units="in", width=10, height=6,  res=300)
print(Fig2)
dev.off()
